### 2023-02-13 article.tex
No chapter in chapter, show abstract
Remove illustration of mismatch between code and text

\chapter{How to make research code useful paradata}

\abstract*{
Paradata is data about the data collection process,
that allows use and reuse of data.
Within the context of computational research,
computer code is the paradata of an experiment,
allowing the study to be reproduced.
A recent study recommended how to make paradata (more) useful,
for paradata in general.
This study applies those recommendations to computer code,
using the field of genetic epidemiology
as an example.
The chapter concludes by some rules how to better code to serve as paradata,
and hence allowing computational research to be more reproducible.
} % abstract

@@

To illustrate how easy it is to get a mismatch between a paper
and the code, 
consider this example of a possible text in the fictional 
genetic epidemiology paper:

@@

Note that there is another side of this same coin:
correctly reporting the t-test in a reproducible ways
is known to be a problem, with only 80 out of a selected 179 papers
fully reporting the parity of t-test (i.e. paired or unpaired) 
\cite{weissgerber2018we}.
In those unresolved 99 papers, 
the code (if published) would clarify this.

>>>>

\abstract{
Paradata is data about the data collection process,
that allows use and reuse of data.
Within the context of computational research,
computer code is the paradata of an experiment,
allowing the study to be reproduced.
A recent study recommended how to make paradata (more) useful,
for paradata in general.
This study applies those recommendations to computer code,
using the field of genetic epidemiology
as an example.
The chapter concludes by some rules how to better code to serve as paradata,
and hence allowing computational research to be more reproducible.
} % abstract

@@

\iffalse
To illustrate how easy it is to get a mismatch between a paper
and the code, 
consider this example of a possible text in the fictional 
genetic epidemiology paper:

@@

Note that there is another side of this same coin:
correctly reporting the t-test in a reproducible ways
is known to be a problem, with only 80 out of a selected 179 papers
fully reporting the parity of t-test (i.e. paired or unpaired) 
\cite{weissgerber2018we}.
In those unresolved 99 papers, 
the code (if published) would clarify this.
\fi
